\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-25 OaklandSubmission/ld.tex
ld first para

\newcommand{\kw}[1]{{\lstinline[basicstyle=\small\color{blue}]{#1}}}
\newcommand{\ftext}[1]{\text{\small{#1}}}
\newcommand{\cond}[3]{\ensuremath{{{#1}\:?\:{#2}\::{#3}}}}
\newcommand{\for}[4]{\ensuremath{\kw{for}\:{#1}\:\kw{in}\:[{#2}, {#3}]\:\kw{do}\:{#4}}}
\newcommand{\ite}[3]{\ensuremath{\kw{if}({#1}, {#2}, {#3})}}
\newcommand{\loops}[3]{\ensuremath{\kw{while}\:{#1} \leq {#2}\:\kw{do}\:{#3}}}

@@

In this section we prove the correctness and security of our compiler.
%
We first formalize the source and target languages. Our source runtime
semantics is a model of the ideal, trusted third-party semantics, and
generates observations corresponding to the values revealed to the
parties.
%
The target language semantics (a model of the C++ code generated by
our compiler implementation) ``computes away'' the public parts and
arrays from the compiled program, generating a secure computation
circuit. Crucially, this semantics does not have access to the secret
inputs--those are processed by the secure computation circuit.
%
Finally, we formalize the circuit semantics that computes the
generated circuit, and like the source semantics, emits observations
corresponding to the values revealed to the parties.

We then present the compilation rules. To prove the correctness
of our compiler, we prove that it preserves the observations. For
security of our compiler, we reduce the security argument to the
security of the cryptographic protocol used to compute the secure
computation circuit.
\nc{Should we also say that security relies on correctness? (they go together)}
We present only selected parts of our formalization for space
reasons. Full definitions and proofs can be found in the supplementary
material submitted along with the paper.

\divya{
In this section we prove the correctness and security of our compiler.
We formalize the source, the intermediate and the circuit languages. 
Our source runtime semantics is a model of the ideal, trusted third-party semantics, and
generates observations corresponding to the values revealed to the
parties.
%
We present the compilation rules that type check a program in the source language and compiles it to a program in the intermediate language.
%
We evaluate the program in our intermediate language (a model of the C++ code generated by our compiler implementation) to a circuit by ``computing away'' the public parts and the arrays. Crucially, this step does not have access to the secret inputs--those are processed by the secure computation circuit.
%
Finally, we formalize the distributed circuit semantics (of the cryptographic back-end) that computes the generated circuit in the distributed setting, and like  the source semantics, emits observations
corresponding to the values revealed to the parties.

To prove the correctness of our compiler, we prove that it preserves the observations in source semantics and distributed circuit semantics (see \theoremref{correctness}). 
For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the
security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization for space
reasons. \TODO{Full definitions and proofs can be found in the supplementary
material submitted along with the paper.}
}

@@

               \hspace{0.1cm}
               \inferrule*[lab={\footnotesize{E-Cond}}]
               {
                 \rho \vdash e \Downarrow c\\\\
                 c = \top \Rightarrow e' = e_{1}\\\\
                 c = \bot \Rightarrow e' = e_{2}\\\\
                 \rho \vdash e \Downarrow c'
               }
               {
                 \rho \vdash \cond{e}{e_{1}}{e_{2}} \Downarrow c'
               }

>>>>

\newcommand{\kw}[1]{{\lstinline[basicstyle=\small\color{blue}]{#1}}}
%\newcommand{\kw}[1]{{\ensuremath{\mathtt{#1}}}}
\newcommand{\ftext}[1]{\text{\small{#1}}}
\newcommand{\cond}[3]{\ensuremath{{{#1}\:?\:{#2}\::{#3}}}}
\newcommand{\for}[4]{\ensuremath{\kw{for}\:{#1}\:\kw{in}\:[{#2}, {#3}]\:\kw{do}\:{#4}}}
\newcommand{\ite}[3]{\ensuremath{\kw{if}({#1}, {#2}, {#3})}}
\newcommand{\loops}[3]{\ensuremath{\kw{while}\:{#1} \leq {#2}\:\kw{do}\:{#3}}}

@@

%In this section we prove the correctness and security of our compiler.
%%
%We first formalize the source and target languages. Our source runtime
%semantics is a model of the ideal, trusted third-party semantics, and
%generates observations corresponding to the values revealed to the
%parties.
%%
%The target language semantics (a model of the C++ code generated by
%our compiler implementation) ``computes away'' the public parts and
%arrays from the compiled program, generating a secure computation
%circuit. Crucially, this semantics does not have access to the secret
%inputs--those are processed by the secure computation circuit.
%%
%Finally, we formalize the circuit semantics that computes the
%generated circuit, and like the source semantics, emits observations
%corresponding to the values revealed to the parties.
%
%We then present the compilation rules. To prove the correctness
%of our compiler, we prove that it preserves the observations. For
%security of our compiler, we reduce the security argument to the
%security of the cryptographic protocol used to compute the secure
%computation circuit.
%\nc{Should we also say that security relies on correctness? (they go together)}
%We present only selected parts of our formalization for space
%reasons. Full definitions and proofs can be found in the supplementary
%material submitted along with the paper.

In this section we prove correctness and security of our compiler \tool.
We formalize our source, intermediate and circuit languages. 
An example of a program in our source language is provided in \figureref{ex-sml}.
%Our source runtime semantics is a model of the ideal, trusted third-party semantics, and
%generates observations corresponding to the values revealed to the
%parties.
Our source runtime semantics describe the standard execution semantics of the source programs and
generates observations corresponding to the values revealed to the
parties.
%
We present the compilation rules that type check a program in the source language and generates a program in the intermediate language. This intermediate language models programs such as \figureref{ex-aby} generated by our compiler implementation.
%
We evaluate the program in our intermediate language  to a circuit by ``computing away'' the public parts and the arrays. Crucially, this step does not have access to the secret inputs--those are processed by the distributed circuit semantics that model the \mpc back-end.
%
Here, the generated circuit is evaluated in the distributed setting, where the parties run an interactive protocol. This step, like  the source semantics, emits observations corresponding to the values revealed to the parties. 
%Finally, we formalize the distributed circuit semantics (of the cryptographic back-end) that computes the generated circuit in the distributed setting, and like  the source semantics, emits observationscorresponding to the values revealed to the parties.

To prove the correctness of \tool, we prove that  the observations in source semantics and distributed circuit semantics are identical (see \theoremref{correctness}). 
We combine this correctness and the security of the \mpc back-end to argue security of the implementations generated by \tool (see \theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization for space
reasons. Full definitions and proofs can be found \cite{anonymized}.

@@

               \hspace{0.1cm}
               \inferrule*[lab={\footnotesize{E-Cond}}]
               {
                 \rho \vdash e \Downarrow c\\\\
                 c = \top \Rightarrow e' = e_{1}\\\\
                 c = \bot \Rightarrow e' = e_{2}\\\\
                 \rho \vdash e' \Downarrow c'
               }
               {
                 \rho \vdash \cond{e}{e_{1}}{e_{2}} \Downarrow c'
               }
